Data Wrangling and Statistical Analysis of Assessment of Abundance, Aggregation, and Web Placement of *Agelenopsis pennsylvanica*

### 2023-01-08 data_analysis.Rmd
Lots of changes

```{r webs_wrangling, include = FALSE}
webs <- webs %>% 
  mutate(ID = factor(ID),
         Location = factor(Location),
         Location = fct_recode(Location, 
                               "Urban Forest" = "Forest",
                               "Urban Center" = "Campus"),
         Location = fct_relevel(Location, 
                                "Urban Forest", "Urban Center"),
         Land = fct_recode(Land, 
                           "Urban, High" = "UrbanizedHighIntensity",
                           "Urban, Medium" = "UrbanizedMediumIntensity",
                           "Urban, Low" = "UrbanizedLowIntensity",
                           "Deciduous Forest" = "DeciduousForest",
                           "Woody Wetlands" = "WoodyWetlands"),
         Land = fct_relevel(Land, 
                            "Urban, High", 
                            "Urban, Medium", 
                            "Urban, Low", 
                            "Deciduous Forest", 
                            "Woody Wetlands"),
         patch_area_km = patch_area_mm * 1e-6) %>% 
  dplyr::rename("Impervious" = "Imperv", 
                "Dist_to_Road" = "road_dist_data", 
                "Traffic_Dist_Road" = "dist_traffic_road", 
                "Dist_to_Highway" = "highway_dist_m", 
                "Traffic_Dist_Highway" = "dist_traffic_highway")

@@

```{r search_land_graph}
sites <- sites %>% 
  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
                            "Woody Wetlands", 
                            "Urban, High", 
                            "Urban, Medium", 
                            "Urban, Low"))
nd <- data.frame(Land = factor(levels(sites$Land)))
predictions <- augment(search_land, newdata = nd, se_fit = TRUE, type.predict = "response")
predictions <- predictions %>% 
  rename("rate" = ".fitted", "SE" = ".se.fit")
#predictions <- summary(emmeans(search_land, ~Land),type = "response")

search_land_plot <- ggplot(sites, aes(x = Land, y = WalkDist)) + 
  geom_jitter(color = "grey", width = 0.1, size = 0.5) +
  geom_point(aes(x = Land, y = rate, color = Land), size = 1, data = predictions) + 
  geom_errorbar(aes(x = Land, 
                  ymin = rate - SE, 
                  ymax = rate + SE, color = Land), data = predictions, inherit.aes = FALSE, width = 0.25, size = 1) +
  theme_classic() +
  scale_color_manual(values = c("Deciduous Forest" = "#1b9e77", "Woody Wetlands" = "#1b9e77", "Urban, High" = "#d95f02", "Urban, Medium" = "#d95f02", "Urban, Low" = "#d95f02")) +
  xlab("Land Cover Class") +
  ylab("Search Distance [m]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x=element_text(colour="black", size=10)) + 
  theme(axis.text.y=element_text(colour="black", size=10)) +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) +
  annotate(geom="text", x=1, y=max(sites$WalkDist), label="A", color="black", size = 3) +
  annotate(geom="text", x=2, y=max(sites$WalkDist), label="B", color="black", size = 3) +
  annotate(geom="text", x=3, y=max(sites$WalkDist), label="C", color="black", size = 3) +
  annotate(geom="text", x=4, y=max(sites$WalkDist), label="A", color="black", size = 3) +
  annotate(geom="text", x=5, y=max(sites$WalkDist), label="A", color="black", size = 3)

@@

```{r webs_land_graph}
sites <- sites %>% 
  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
                            "Woody Wetlands", 
                            "Urban, High", 
                            "Urban, Medium", 
                            "Urban, Low"))
nd <- data.frame(Land = factor(levels(sites$Land)))
predictions <- augment(webs_land, newdata = nd, se_fit = TRUE, type.predict = "response")
predictions <- predictions %>% 
  rename("rate" = ".fitted", "SE" = ".se.fit")
#predictions <- summary(emmeans(webs_land, ~Land),type = "response")

webs_land_plot <- ggplot(sites, aes(x = Land, y = NumWebs)) + 
  geom_jitter(color = "grey", width = 0.1, size = 0.5) +
  geom_point(aes(x = Land, y = rate, color = Land), size = 1, data = predictions) + 
  geom_errorbar(aes(x = Land, 
                  ymin = rate - SE, 
                  ymax = rate + SE, color = Land), data = predictions, inherit.aes = FALSE, width = 0.25, size = 1) +
  theme_classic() +
  scale_color_manual(values = c("Deciduous Forest" = "#1b9e77", "Woody Wetlands" = "#1b9e77", "Urban, High" = "#d95f02", "Urban, Medium" = "#d95f02", "Urban, Low" = "#d95f02")) +
  xlab("Land Cover Class") +
  ylab("Number of Webs") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x=element_text(colour="black", size=10)) + 
  theme(axis.text.y=element_text(colour="black", size=10)) +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) +
  annotate(geom="text", x=1, y=max(sites$NumWebs), label="A", color="black", size = 3) +
  annotate(geom="text", x=2, y=max(sites$NumWebs), label="A", color="black", size = 3) +
  annotate(geom="text", x=3, y=max(sites$NumWebs), label="B", color="black", size = 3) +
  annotate(geom="text", x=4, y=max(sites$NumWebs), label="B", color="black", size = 3) +
  annotate(geom="text", x=5, y=max(sites$NumWebs), label="B", color="black", size = 3)

@@

```{r spiders_land_graph}
sites <- sites %>% 
  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
                            "Woody Wetlands", 
                            "Urban, High", 
                            "Urban, Medium", 
                            "Urban, Low"))
nd <- data.frame(Land = factor(levels(sites$Land)))
predictions <- augment(spiders_land, newdata = nd, se_fit = TRUE, type.predict = "response")
predictions <- predictions %>% 
  rename("rate" = ".fitted", "SE" = ".se.fit")
#predictions <- summary(emmeans(spiders_land, ~Land),type = "response")

spiders_land_plot <- ggplot(sites, aes(x = Land, y = NumSpiders)) + 
  geom_jitter(color = "grey", width = 0.1, size = 0.5) +
  geom_point(aes(x = Land, y = rate, color = Land), size = 1, data = predictions) + 
  geom_errorbar(aes(x = Land, 
                  ymin = rate - SE, 
                  ymax = rate + SE, color = Land), data = predictions, inherit.aes = FALSE, width = 0.25, size = 1) +
  theme_classic() +
  scale_color_manual(values = c("Deciduous Forest" = "#1b9e77", "Woody Wetlands" = "#1b9e77", "Urban, High" = "#d95f02", "Urban, Medium" = "#d95f02", "Urban, Low" = "#d95f02")) +
  xlab("Land Cover Class") +
  ylab("Number of Spiders") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x=element_text(colour="black", size=10)) + 
  theme(axis.text.y=element_text(colour="black", size=10)) +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) +
  annotate(geom="text", x=1, y=max(sites$NumSpiders), label="A", color="black", size = 3) +
  annotate(geom="text", x=2, y=max(sites$NumSpiders), label="A", color="black", size = 3) +
  annotate(geom="text", x=3, y=max(sites$NumSpiders), label="B", color="black", size = 3) +
  annotate(geom="text", x=4, y=max(sites$NumSpiders), label="B", color="black", size = 3) +
  annotate(geom="text", x=5, y=max(sites$NumSpiders), label="B", color="black", size = 3)

@@

raw_plot_dist <- ggplot(web_dist, aes(x = Neighbor, y = RetreatDist)) + 
  geom_jitter(color = "grey", width = 0.1) +
  geom_point(aes(x = Neighbor, y = mean, color = Location), size = 2, data = raw) +
  geom_line(aes(x = Neighbor, y = mean, group = Location), size = 2, data = raw, color = "grey") +
  geom_errorbar(aes(x= Neighbor, 
                    ymin = mean - se, 
                    ymax = mean + se, 
                    color = Location), data = raw, inherit.aes = FALSE, width = 0.15, size = 1.5) +
    scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
    scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
    theme_classic() +
    scale_y_continuous(limits = c(0, 1000), breaks = c(0, 200, 400, 600, 800, 1000)) +
    xlab("Nearest Neighbors") +
    ylab("Distance from Focal Web \nto Neighbor Web [cm]") + 
    theme(text = element_text(size = 10)) + 
    theme(axis.text.x = element_text(colour = "black", size = 10)) + 
    theme(axis.text.y = element_text(colour = "black", size = 10)) +
    theme(legend.position = "none")

@@

poisson_plot_dist <- ggplot(web_dist, aes(x = Neighbor, y = RetreatDist)) + 
  geom_jitter(color = "grey", width = 0.1) +
  geom_point(aes(x = Neighbor, y = response, color = Location), size = 2, data = predictions) + 
  geom_line(aes(x = Neighbor, y = response, group = Location), size = 2, data = predictions, color = "grey") +
  geom_errorbar(aes(x = Neighbor, 
                  ymin = response - SE, 
                  ymax = response + SE,
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  theme_classic() +
  scale_y_continuous(limits = c(0, 1000), breaks = c(0, 200, 400, 600, 800, 1000)) +
  xlab("Nearest Neighbors") +
  ylab("Distance from Focal Web \nto Neighbor Web [cm]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
  theme(axis.text.y = element_text(colour = "black", size = 10)) +
  theme(legend.position = "none")

@@

log_plot_dist <- ggplot(web_dist, aes(x = Neighbor, y = (RetreatDist))) + 
  geom_jitter(color = "grey", width = 0.1) +
  geom_point(aes(x = Neighbor, y = exp(response), color = Location), size = 2, data = predictions) + 
  geom_line(aes(x = Neighbor, y = exp(response), group = Location), size = 2, data = predictions, color = "grey") +
  geom_errorbar(aes(x = Neighbor, 
                  ymin = exp(response - SE), 
                  ymax = exp(response + SE),
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  theme_classic() +
  scale_y_continuous(limits = c(0, 1000), breaks = c(0, 200, 400, 600, 800, 1000)) +
  xlab("Nearest Neighbors") +
  ylab("Distance from Focal Web \nto Neighbor Web [cm]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
  theme(axis.text.y = element_text(colour = "black", size = 10))

@@

```{r dist_land_graph}
near <- near %>% 
  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
                            "Woody Wetlands", 
                            "Urban, High", 
                            "Urban, Medium", 
                            "Urban, Low"))
nd <- data.frame(Land = factor(levels(sites$Land)))
predictions <- augment(dist_land, newdata = nd, se_fit = TRUE, type.predict = "response")
predictions <- predictions %>% 
  rename("response" = ".fitted", "SE" = ".se.fit")
#predictions <- summary(emmeans(dist_land, ~Land),type = "response")

@@

```{r height_land_graph}
webs <- webs %>% 
  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
                            "Woody Wetlands", 
                            "Urban, High", 
                            "Urban, Medium", 
                            "Urban, Low"))
predictions <- expand.grid(Land = levels(factor(webs$Land)))
predictions$response <- predict(height_land, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")

@@

predictors_agg <- ggarrange(agg1, labels1, agg2, labels2, nrow = 4, heights = c(0.35, 0.15, 0.35, 0.15))
#saveRDS(predictors_agg, "manuscript/figures/predictors_agg.Rds")
```

@@

```{r landscape_table}
rownames(land_cover) <- c("Area (sq. km)", "Tree Cover (%)", "Impervious Cover (%)", "Urban Cover (%)", "Urban, High Intensity (%)", "Urban, Medium Intensity (%)", "Urban, low Intensity (%)", "Urban, Open Space (%)", "Forest Cover (%)", "Deciduous Forest (%)", "Mixed Forest (%)", "Evergreen Forest (%)", "Woody Wetlands (%)", "Other Cover (%)", "Herbaceous Wetlands (%)", "Grassland Herbaceous (%)", "Pasture (%)", "Cultivated Crop (%)", "Open Water (%)")
names <- rownames(land_cover)
rownames(land_cover) <- seq(1:nrow(land_cover))
land_cover <- cbind(names, land_cover)
colnames(land_cover) <- c(" ", "Lincoln City Limits", "UNL City Campus \nUrban Center", "Wilderness Park \nUrban Forest")
flextable(land_cover[ ,1:4]) %>% 
  autofit() %>% 
  hline(i = c("3", "4", "8", "9", "13", "14"), part = "body") %>% 
  bg(i = c("4", "9", "14"), bg = "grey95") %>% 
  bold(bold = TRUE, part = "header") %>% 
  fontsize(size = 10, part = "all") %>% 
  align(align = "center", part = "all") %>% 
  set_caption("") %>% 
  save_as_image(path = here::here("manuscript/figures/landscape.png"))
```

@@

```{r pred_location, fig.width = 6.85, dpi = 300}
mean_se1 <- c("Mean ± Std. Error", "Wilderness Park \nUrban Forest", "47.15 ± 2.17", "1.27 ± 0.36", "137.44 ± 3.71", "5.89 ± 0.77", "13.30 ± 1.15", "46,294.7 ± 68.040", "104 ± 3.23", "35.6 ± 1.89", "15.67 ± 1.25")
mean_se2 <- c("Mean ± Std. Error", "UNL City Campus \n Urban Center", "1.58 ± 0.36", "76.52 ± 2.53", "153.39 ± 3.58", "116.90 ± 3.12", "3.33 ± 0.53", "116.90 ± 3.12", "398 ± 5.76", "65.0 ± 2.33", "93.03 ± 2.78")
pred_location <- data.frame(mean_se1, mean_se2)
rownames(pred_location) <- c("", " ", "Percent Tree Cover [%]", "Percent Impervious Cover [%]", "Spectral Radiance [Watts/(m² * sr * µm)]", "Artificial Night Sky Radiance [mcd/m²]", "Plant Species Richness", "Patch Area [m²]", "Road Disturbance [vehicles/day/m]", "Highway Disturbance [vehicles/day/m]", "Total Road Length [m]")
names <- rownames(pred_location)
rownames(pred_location) <- seq(1:nrow(pred_location))
pred_location <- cbind(names, pred_location)
colnames(pred_location) <- c(" ", "Mean ± Std. Error", "Mean ± Std. Error")
flextable(pred_location[ ,1:3]) %>% 
  delete_part(part = "header") %>% 
  autofit() %>% 
  merge_h(part = "body") %>% 
  bold(bold = TRUE,i = c("1", "2"), part = "body") %>% 
  hline(i = c("1", "2", "11"), part = "body", border = officer::fp_border(width = 2)) %>% 
  hline_top(part = "body", border = officer::fp_border(width = 2)) %>% 
  fontsize(size = 10, part = "all") %>% 
  align(align = "center", part = "all") %>% 
  set_caption("") %>% 
  save_as_image(path = here::here("manuscript/figures/pred_location.png"))
```

@@

```{r substrate}
substrates %>% 
  mutate(Location = fct_recode(Location, "Urban Center" = "Campus", "Urban Forest" = "Forest"),
         Location = fct_relevel(Location, "Urban Forest", "Urban Center")) %>% 
  ggplot(aes(x = Location, y = Number, fill = factor(Type, levels=c("Cement", "Metal", "Plastic", "Rocks", "Herb", "Litter", "Shrub", "Tree", "Vine")))) + 
  geom_bar(position = "fill",stat = "identity", alpha=1.0) + 
  scale_y_continuous(labels = scales::percent_format()) + 
  theme(axis.title.x = element_blank()) + 
  xlab("Collection Location") +
  ylab("Percent of Web Substrates") + 
  theme_classic() +
  theme(text = element_text(size = 10)) + 
  scale_fill_manual(values = c("#D94701", "#FD8D3C", "#FDBE85", "#FEEDDE", "#006D2C", "#31A354", "#74C476", "#BAE4B3", "#EDF8E9"), 
                    labels = c("Cement", "Metal", "Plastic", "Rocks", "Herb", "Litter", "Shrub", "Tree", "Vine")) + 
  labs(fill="Substrate Material") + 
  theme(axis.text.x=element_text(colour="black", size=10)) + 
  theme(axis.text.y=element_text(colour="black", size=10)) +
  theme(legend.text=element_text(size=10))
  ggsave("manuscript/figures/substrate_plot.png")
```

>>>>

```{r webs_wrangling, include = FALSE}
webs <- webs %>% 
  mutate(ID = factor(ID),
         Location = factor(Location),
         Location = fct_recode(Location, 
                               "Urban Forest" = "Forest",
                               "Urban Center" = "Campus"),
         Location = fct_relevel(Location, 
                                "Urban Center", "Urban Forest"),
         Land = fct_recode(Land, 
                           "Urban, High" = "UrbanizedHighIntensity",
                           "Urban, Medium" = "UrbanizedMediumIntensity",
                           "Urban, Low" = "UrbanizedLowIntensity",
                           "Deciduous Forest" = "DeciduousForest",
                           "Woody Wetlands" = "WoodyWetlands"),
         Land = fct_relevel(Land, 
                            "Urban, High", 
                            "Urban, Medium", 
                            "Urban, Low", 
                            "Deciduous Forest", 
                            "Woody Wetlands"),
         patch_area_km = patch_area_mm * 1e-6) %>% 
  dplyr::rename("Impervious" = "Imperv", 
                "Dist_to_Road" = "road_dist_data", 
                "Traffic_Dist_Road" = "dist_traffic_road", 
                "Dist_to_Highway" = "highway_dist_m", 
                "Traffic_Dist_Highway" = "dist_traffic_highway")

@@

```{r search_land_graph}
#sites <- sites %>% 
#  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
#                            "Woody Wetlands", 
#                            "Urban, High", 
#                            "Urban, Medium", 
#                            "Urban, Low"))
nd <- data.frame(Land = factor(levels(sites$Land)))
predictions <- augment(search_land, newdata = nd, se_fit = TRUE, type.predict = "response")
predictions <- predictions %>% 
  rename("rate" = ".fitted", "SE" = ".se.fit")
#predictions <- summary(emmeans(search_land, ~Land),type = "response")

search_land_plot <- ggplot(sites, aes(x = Land, y = WalkDist)) + 
  geom_jitter(color = "grey", width = 0.1, size = 0.5) +
  geom_point(aes(x = Land, y = rate, color = Land), size = 1, data = predictions) + 
  geom_errorbar(aes(x = Land, 
                  ymin = rate - SE, 
                  ymax = rate + SE, color = Land), data = predictions, inherit.aes = FALSE, width = 0.25, size = 1) +
  theme_classic() +
  scale_color_manual(values = c("Deciduous Forest" = "#1b9e77", "Woody Wetlands" = "#1b9e77", "Urban, High" = "#d95f02", "Urban, Medium" = "#d95f02", "Urban, Low" = "#d95f02")) +
  xlab("Land Cover Class") +
  ylab("Search Distance [m]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x=element_text(colour="black", size=10)) + 
  theme(axis.text.y=element_text(colour="black", size=10)) +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) +
  annotate(geom="text", x=1, y=max(sites$WalkDist), label="A", color="black", size = 3) +
  annotate(geom="text", x=2, y=max(sites$WalkDist), label="B", color="black", size = 3) +
  annotate(geom="text", x=3, y=max(sites$WalkDist), label="B", color="black", size = 3) +
  annotate(geom="text", x=4, y=max(sites$WalkDist), label="B", color="black", size = 3) +
  annotate(geom="text", x=5, y=max(sites$WalkDist), label="C", color="black", size = 3)

@@

```{r webs_land_graph}
#sites <- sites %>% 
#  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
#                            "Woody Wetlands", 
#                            "Urban, High", 
#                            "Urban, Medium", 
#                            "Urban, Low"))
nd <- data.frame(Land = factor(levels(sites$Land)))
predictions <- augment(webs_land, newdata = nd, se_fit = TRUE, type.predict = "response")
predictions <- predictions %>% 
  rename("rate" = ".fitted", "SE" = ".se.fit")
#predictions <- summary(emmeans(webs_land, ~Land),type = "response")

webs_land_plot <- ggplot(sites, aes(x = Land, y = NumWebs)) + 
  geom_jitter(color = "grey", width = 0.1, size = 0.5) +
  geom_point(aes(x = Land, y = rate, color = Land), size = 1, data = predictions) + 
  geom_errorbar(aes(x = Land, 
                  ymin = rate - SE, 
                  ymax = rate + SE, color = Land), data = predictions, inherit.aes = FALSE, width = 0.25, size = 1) +
  theme_classic() +
  scale_color_manual(values = c("Deciduous Forest" = "#1b9e77", "Woody Wetlands" = "#1b9e77", "Urban, High" = "#d95f02", "Urban, Medium" = "#d95f02", "Urban, Low" = "#d95f02")) +
  xlab("Land Cover Class") +
  ylab("Number of Webs") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x=element_text(colour="black", size=10)) + 
  theme(axis.text.y=element_text(colour="black", size=10)) +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) +
  annotate(geom="text", x=1, y=max(sites$NumWebs), label="A", color="black", size = 3) +
  annotate(geom="text", x=2, y=max(sites$NumWebs), label="A", color="black", size = 3) +
  annotate(geom="text", x=3, y=max(sites$NumWebs), label="A", color="black", size = 3) +
  annotate(geom="text", x=4, y=max(sites$NumWebs), label="B", color="black", size = 3) +
  annotate(geom="text", x=5, y=max(sites$NumWebs), label="B", color="black", size = 3)

@@

```{r spiders_land_graph}
#sites <- sites %>% 
#  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
#                            "Woody Wetlands", 
#                            "Urban, High", 
#                            "Urban, Medium", 
#                            "Urban, Low"))
nd <- data.frame(Land = factor(levels(sites$Land)))
predictions <- augment(spiders_land, newdata = nd, se_fit = TRUE, type.predict = "response")
predictions <- predictions %>% 
  rename("rate" = ".fitted", "SE" = ".se.fit")
#predictions <- summary(emmeans(spiders_land, ~Land),type = "response")

spiders_land_plot <- ggplot(sites, aes(x = Land, y = NumSpiders)) + 
  geom_jitter(color = "grey", width = 0.1, size = 0.5) +
  geom_point(aes(x = Land, y = rate, color = Land), size = 1, data = predictions) + 
  geom_errorbar(aes(x = Land, 
                  ymin = rate - SE, 
                  ymax = rate + SE, color = Land), data = predictions, inherit.aes = FALSE, width = 0.25, size = 1) +
  theme_classic() +
  scale_color_manual(values = c("Deciduous Forest" = "#1b9e77", "Woody Wetlands" = "#1b9e77", "Urban, High" = "#d95f02", "Urban, Medium" = "#d95f02", "Urban, Low" = "#d95f02")) +
  xlab("Land Cover Class") +
  ylab("Number of Spiders") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x=element_text(colour="black", size=10)) + 
  theme(axis.text.y=element_text(colour="black", size=10)) +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) +
  annotate(geom="text", x=1, y=max(sites$NumSpiders), label="A", color="black", size = 3) +
  annotate(geom="text", x=2, y=max(sites$NumSpiders), label="A", color="black", size = 3) +
  annotate(geom="text", x=3, y=max(sites$NumSpiders), label="A", color="black", size = 3) +
  annotate(geom="text", x=4, y=max(sites$NumSpiders), label="B", color="black", size = 3) +
  annotate(geom="text", x=5, y=max(sites$NumSpiders), label="B", color="black", size = 3)

@@

raw_plot_dist <- ggplot(web_dist, aes(x = Neighbor, y = RetreatDist)) + 
  geom_jitter(color = "grey", width = 0.1) +
  geom_point(aes(x = Neighbor, y = mean, color = Location), size = 2, data = raw) +
  geom_line(aes(x = Neighbor, y = mean, group = Location), size = 2, data = raw, color = "grey") +
  geom_errorbar(aes(x= Neighbor, 
                    ymin = mean - se, 
                    ymax = mean + se, 
                    color = Location), data = raw, inherit.aes = FALSE, width = 0.15, size = 1.5) +
    scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
    scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
    theme_classic() +
    scale_y_continuous(limits = c(-50, 1000), breaks = c(0, 200, 400, 600, 800, 1000)) +
    xlab("Nearest Neighbors") +
    ylab("Distance from Focal Web \nto Neighbor Web [cm]") + 
    theme(text = element_text(size = 10)) + 
    theme(axis.text.x = element_text(colour = "black", size = 10)) + 
    theme(axis.text.y = element_text(colour = "black", size = 10)) +
    theme(legend.position = "none")

@@

poisson_plot_dist <- ggplot(web_dist, aes(x = Neighbor, y = RetreatDist)) + 
  geom_jitter(color = "grey", width = 0.1) +
  geom_point(aes(x = Neighbor, y = response, color = Location), size = 2, data = predictions) + 
  geom_line(aes(x = Neighbor, y = response, group = Location), size = 2, data = predictions, color = "grey") +
  geom_errorbar(aes(x = Neighbor, 
                  ymin = response - SE, 
                  ymax = response + SE,
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  theme_classic() +
  scale_y_continuous(limits = c(-50, 1000), breaks = c(0, 200, 400, 600, 800, 1000)) +
  xlab("Nearest Neighbors") +
  ylab("Distance from Focal Web \nto Neighbor Web [cm]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
  theme(axis.text.y = element_text(colour = "black", size = 10)) +
  theme(legend.position = "none")

@@

log_plot_dist <- ggplot(web_dist, aes(x = Neighbor, y = (RetreatDist))) + 
  geom_jitter(color = "grey", width = 0.1) +
  geom_point(aes(x = Neighbor, y = exp(response), color = Location), size = 2, data = predictions) + 
  geom_line(aes(x = Neighbor, y = exp(response), group = Location), size = 2, data = predictions, color = "grey") +
  geom_errorbar(aes(x = Neighbor, 
                  ymin = exp(response - SE), 
                  ymax = exp(response + SE),
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  theme_classic() +
  scale_y_continuous(limits = c(-50, 1000), breaks = c(0, 200, 400, 600, 800, 1000)) +
  xlab("Nearest Neighbors") +
  ylab("Distance from Focal Web \nto Neighbor Web [cm]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
  theme(axis.text.y = element_text(colour = "black", size = 10))

@@

```{r dist_land_graph}
#near <- near %>% 
#  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
#                            "Woody Wetlands", 
#                            "Urban, High", 
#                            "Urban, Medium", 
#                            "Urban, Low"))
nd <- data.frame(Land = factor(levels(sites$Land)))
predictions <- augment(dist_land, newdata = nd, se_fit = TRUE, type.predict = "response")
predictions <- predictions %>% 
  rename("response" = ".fitted", "SE" = ".se.fit")
#predictions <- summary(emmeans(dist_land, ~Land),type = "response")

@@

```{r height_land_graph}
#webs <- webs %>% 
#  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
#                            "Woody Wetlands", 
#                            "Urban, High", 
#                            "Urban, Medium", 
#                            "Urban, Low"))
predictions <- expand.grid(Land = levels(factor(webs$Land)))
predictions$response <- predict(height_land, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")

@@

predictors_agg <- ggarrange(agg2, labels2, agg1, labels1, nrow = 4, heights = c(0.35, 0.15, 0.35, 0.15))
#saveRDS(predictors_agg, "manuscript/figures/predictors_agg.Rds")
```

@@

```{r landscape_table}
rownames(land_cover) <- c("Area (sq. km)", "Tree Cover (%)", "Impervious Cover (%)", "Urban Cover (%)", "Urban, High Intensity (%)", "Urban, Medium Intensity (%)", "Urban, low Intensity (%)", "Urban, Open Space (%)", "Forest Cover (%)", "Deciduous Forest (%)", "Mixed Forest (%)", "Evergreen Forest (%)", "Woody Wetlands (%)", "Other Cover (%)", "Herbaceous Wetlands (%)", "Grassland Herbaceous (%)", "Pasture (%)", "Cultivated Crop (%)", "Open Water (%)")
names <- rownames(land_cover)
rownames(land_cover) <- seq(1:nrow(land_cover))
land_cover <- cbind(names, land_cover)
colnames(land_cover) <- c(" ", "Urban Center \n(UNL City Campus)", "Urban Forest \n(Wilderness Park)", "Lincoln City Limits")
flextable(land_cover[ ,1:4]) %>% 
  autofit() %>% 
  hline(i = c("3", "4", "8", "9", "13", "14"), part = "body") %>% 
  bg(i = c("4", "9", "14"), bg = "grey95") %>% 
  bold(bold = TRUE, part = "header") %>% 
  fontsize(size = 10, part = "all") %>% 
  align(align = "center", part = "all") %>% 
  set_caption("") %>% 
  save_as_image(path = here::here("manuscript/figures/landscape.png"))
```

@@

```{r pred_location, fig.width = 6.85, dpi = 300}
mean_se1 <- c("Mean ± Std. Error", "Urban Forest \n(Wilderness Park)", "47.15 ± 2.17", "1.27 ± 0.36", "137.44 ± 3.71", "5.89 ± 0.77", "13.30 ± 1.15", "46,294.7 ± 68.040", "104 ± 3.23", "35.6 ± 1.89", "15.67 ± 1.25")
mean_se2 <- c("Mean ± Std. Error", "Urban Center \n(UNL City Campus)", "1.58 ± 0.36", "76.52 ± 2.53", "153.39 ± 3.58", "116.90 ± 3.12", "3.33 ± 0.53", "116.90 ± 3.12", "398 ± 5.76", "65.0 ± 2.33", "93.03 ± 2.78")
pred_location <- data.frame(mean_se2, mean_se1)
rownames(pred_location) <- c("", " ", "Percent Tree Cover [%]", "Percent Impervious Cover [%]", "Spectral Radiance [Watts/(m² * sr * µm)]", "Artificial Night Sky Radiance [mcd/m²]", "Plant Species Richness", "Patch Area [m²]", "Road Disturbance [vehicles/day/m]", "Highway Disturbance [vehicles/day/m]", "Total Road Length [m]")
names <- rownames(pred_location)
rownames(pred_location) <- seq(1:nrow(pred_location))
pred_location <- cbind(names, pred_location)
colnames(pred_location) <- c(" ", "Mean ± Std. Error", "Mean ± Std. Error")
flextable(pred_location[ ,1:3]) %>% 
  delete_part(part = "header") %>% 
  autofit() %>% 
  merge_h(part = "body") %>% 
  bold(bold = TRUE,i = c("1", "2"), part = "body") %>% 
  hline(i = c("1", "2", "11"), part = "body", border = officer::fp_border(width = 2)) %>% 
  hline_top(part = "body", border = officer::fp_border(width = 2)) %>% 
  fontsize(size = 10, part = "all") %>% 
  align(align = "center", part = "all") %>% 
  set_caption("") %>% 
  save_as_image(path = here::here("manuscript/figures/pred_location.png"))
```

@@

```{r substrate}
substrates %>% 
  mutate(Location = fct_recode(Location, "Urban Center" = "Campus", "Urban Forest" = "Forest"),
         Location = fct_relevel(Location, "Urban Center", "Urban Forest")) %>% 
  ggplot(aes(x = Location, y = Number, fill = factor(Type, levels=c("Cement", "Metal", "Plastic", "Rocks", "Herb", "Litter", "Shrub", "Tree", "Vine")))) + 
  geom_bar(position = "fill",stat = "identity", alpha=1.0) + 
  scale_y_continuous(labels = scales::percent_format()) + 
  theme(axis.title.x = element_blank()) + 
  xlab("Collection Location") +
  ylab("Percent of Web Substrates") + 
  theme_classic() +
  theme(text = element_text(size = 10)) + 
  scale_fill_manual(values = c("#D94701", "#FD8D3C", "#FDBE85", "#FEEDDE", "#006D2C", "#31A354", "#74C476", "#BAE4B3", "#EDF8E9"), 
                    labels = c("Cement", "Metal", "Plastic", "Rocks", "Herb", "Litter", "Shrub", "Tree", "Vine")) + 
  labs(fill="Substrate Material") + 
  theme(axis.text.x=element_text(colour="black", size=10)) + 
  theme(axis.text.y=element_text(colour="black", size=10)) +
  theme(legend.text=element_text(size=10))
  ggsave("manuscript/figures/substrate_plot.png")
```
